---
title: "unused plots and code"
output: html_notebook
---

###################################################FOR GTEX RESULTS##########################################################
# Performance and Sample Size {.tabset .tabset-fade .tabset-pills}

## log<sub>2</sub>(auPRC/prior) {.tabset .tabset-fade .tabset-pills}

### Naive Standard
```{r echo=FALSE}
l2_auprc_prior_ss_plot <- gnr %>% 
  ggplot(aes(x = sample_num, y = log2_auprc_over_prior, color = method)) +
  geom_point() +
  xlab("Sample Number") +
  ylab("log2(auPRC/prior)") +
  scale_x_continuous(breaks = c(0,500,1000,1500), labels = c("0","500","1000","1500"), limits = c(0,1500)) +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_auprc_prior_ss_plot)
```

```{r echo=FALSE}
l2_auprc_prior_ss_cors <- gnr %>% 
  group_by(method) %>% 
  summarise(correlation = cor(log2_auprc_over_prior, sample_num, method = "pearson"))

datatable(l2_auprc_prior_ss_cors, rownames = FALSE, filter="top", options = list(pageLength = 10, scrollX=T), 
          colnames = c("Method", "Pearson Correlation of log2(auPRC/prior) and Sample Number"))
```

### Tissue Specific Standards
```{r echo=FALSE}
l2_auprc_prior_ss_plot_ts <- gkr %>% 
  ggplot(aes(x = sample_num, y = log2_auprc_over_prior, color = method)) +
  geom_point() +
  xlab("Sample Number") +
  ylab("log2(auPRC/prior)") +
  scale_x_continuous(breaks = c(0,500,1000,1500), labels = c("0","500","1000","1500"), limits = c(0,1500)) +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_auprc_prior_ss_plot_ts)
```

```{r echo=FALSE}
l2_auprc_prior_ss_cors_ts <- gkr %>% 
  group_by(method) %>% 
  summarise(correlation = cor(log2_auprc_over_prior, sample_num, method = "pearson"))

datatable(l2_auprc_prior_ss_cors_ts, rownames = FALSE, filter="top", options = list(pageLength = 10, scrollX=T), 
          colnames = c("Method", "Pearson Correlation of log2(auPRC/prior) and Sample Number"))
```

## auROC {.tabset .tabset-fade .tabset-pills}

### Naive Standard
```{r echo=FALSE}
l2_auroc_ss_plot <- gnr %>% 
  ggplot(aes(x = sample_num, y = auROC, color = method)) +
  geom_point() +
  xlab("Sample Number") +
  ylab("auROC") +
  scale_x_continuous(breaks = c(0,500,1000,1500), labels = c("0","500","1000","1500"), limits = c(0,1500)) +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_auroc_ss_plot)
```

```{r echo=FALSE}
l2_auroc_ss_cors <- gnr %>% 
  group_by(method) %>% 
  summarise(correlation = cor(auROC, sample_num, method = "pearson"))

datatable(l2_auroc_ss_cors, rownames = FALSE, filter="top", options = list(pageLength = 10, scrollX=T), 
          colnames = c("Method", "Pearson Correlation of auROC and Sample Number"))
```

### Tissue Specific Standards
```{r echo=FALSE}
l2_auroc_ss_plot_ts <- gkr %>% 
  ggplot(aes(x = sample_num, y = auROC, color = method)) +
  geom_point() +
  xlab("Sample Number") +
  ylab("auROC") +
  scale_x_continuous(breaks = c(0,500,1000,1500), labels = c("0","500","1000","1500"), limits = c(0,1500)) +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_auroc_ss_plot_ts)
```

```{r echo=FALSE}
l2_auroc_ss_cors_ts <- gkr %>% 
  group_by(method) %>% 
  summarise(correlation = cor(auROC, sample_num, method = "pearson"))

datatable(l2_auroc_ss_cors_ts, rownames = FALSE, filter="top", options = list(pageLength = 10, scrollX=T), 
          colnames = c("Method", "Pearson Correlation of auROC and Sample Number"))
```

## log<sub>2</sub>(precision/prior) at 20% recall {.tabset .tabset-fade .tabset-pills}

```{r include=FALSE}
tmp <- gnr %>% select(dataset, sample_num, median_spearman, counts_sample_sums_median, counts_sample_sums_variance)
lrg_gnpr <- left_join(gnpr, tmp, by = "dataset")

tmp <- gkr %>% select(dataset, sample_num, median_spearman, counts_sample_sums_median, counts_sample_sums_variance)
lrg_gkpr <- left_join(gkpr, tmp, by = "dataset")
```

### Naive Standard
```{r echo=FALSE}
l2_prec_at_recall20_ss_plot <- lrg_gnpr %>% 
  ggplot(aes(x = sample_num, y = log2_precision_over_prior, color = method)) +
  geom_point() +
  xlab("Sample Number") +
  ylab("log2(precision/prior) at 20% recall") +
  scale_x_continuous(breaks = c(0,500,1000,1500), labels = c("0","500","1000","1500"), limits = c(0,1500)) +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_prec_at_recall20_ss_plot)
```

```{r echo=FALSE}
l2_prec_at_recall20_ss_cors <- lrg_gnpr %>% 
  group_by(method) %>% 
  summarise(correlation = cor(log2_precision_over_prior, sample_num, method = "pearson"))

datatable(l2_prec_at_recall20_ss_cors, rownames = FALSE, filter="top", options = list(pageLength = 10, scrollX=T), 
          colnames = c("Method", "Pearson Correlation of log2(precision/prior) at 20% recall and Sample Number"))
```

### Tissue Specific Standards
```{r echo=FALSE}
l2_prec_at_recall20_ss_plot_ts <- lrg_gkpr %>% 
  ggplot(aes(x = sample_num, y = log2_precision_over_prior, color = method)) +
  geom_point() +
  xlab("Sample Number") +
  ylab("log2(precision/prior) at 20% recall") +
  scale_x_continuous(breaks = c(0,500,1000,1500), labels = c("0","500","1000","1500"), limits = c(0,1500)) +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_prec_at_recall20_ss_plot_ts)
```

```{r echo=FALSE}
l2_prec_at_recall20_ss_cors_ts <- lrg_gkpr %>% 
  group_by(method) %>% 
  summarise(correlation = cor(log2_precision_over_prior, sample_num, method = "pearson"))

datatable(l2_prec_at_recall20_ss_cors_ts, rownames = FALSE, filter="top", options = list(pageLength = 10, scrollX=T), 
          colnames = c("Method", "Pearson Correlation of log2(precision/prior) at 20% recall and Sample Number"))
```

# Performance and Sample Gene Expression Similarity {.tabset .tabset-fade .tabset-pills}
Sample similarity was calculated by taking the median pairwise spearman correlation of the samples in each experiment. The expression of the 50% most variable genes in each tissue were used in correlation calculation.

## log<sub>2</sub>(auPRC/prior) {.tabset .tabset-fade .tabset-pills}

### Naive Standard
```{r echo=FALSE}
l2_auprc_prior_sexps_plot <- gnr %>% 
  ggplot(aes(x = median_spearman, y = log2_auprc_over_prior, color = method)) +
  geom_point() +
  xlab("Sample Similarity") +
  ylab("log2(auPRC/prior)") +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_auprc_prior_sexps_plot)
```

```{r echo=FALSE}
l2_auprc_prior_sexps_cors <- gnr %>% 
  group_by(method) %>% 
  summarise(correlation = cor(log2_auprc_over_prior, median_spearman, method = "pearson"))

datatable(l2_auprc_prior_sexps_cors, rownames = FALSE, filter="top", options = list(pageLength = 10, scrollX=T), 
          colnames = c("Method", "Pearson Correlation of log2(auPRC/prior) and Sample Similarity"))
```

### Tissue Specific Standards
```{r echo=FALSE}
l2_auprc_prior_sexps_plot_ts <- gkr %>% 
  ggplot(aes(x = median_spearman, y = log2_auprc_over_prior, color = method)) +
  geom_point() +
  xlab("Sample Similarity") +
  ylab("log2(auPRC/prior)") +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_auprc_prior_sexps_plot_ts)
```

```{r echo=FALSE}
l2_auprc_prior_sexps_cors_ts <- gkr %>% 
  group_by(method) %>% 
  summarise(correlation = cor(log2_auprc_over_prior, median_spearman, method = "pearson"))

datatable(l2_auprc_prior_sexps_cors_ts, rownames = FALSE, filter="top", options = list(pageLength = 10, scrollX=T), 
          colnames = c("Method", "Pearson Correlation of log2(auPRC/prior) and Sample Similarity"))
```

## auROC {.tabset .tabset-fade .tabset-pills}

### Naive Standard
```{r echo=FALSE}
l2_auroc_sexps_plot <- gnr %>% 
  ggplot(aes(x = median_spearman, y = auROC, color = method)) +
  geom_point() +
  xlab("Sample Similarity") +
  ylab("auROC") +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_auroc_sexps_plot)
```

```{r echo=FALSE}
l2_auroc_sexps_cors <- gnr %>% 
  group_by(method) %>% 
  summarise(correlation = cor(auROC, median_spearman, method = "pearson"))

datatable(l2_auroc_sexps_cors, rownames = FALSE, filter="top", options = list(pageLength = 10, scrollX=T), 
          colnames = c("Method", "Pearson Correlation of auROC and Sample Similarity"))
```

### Tissue Specific Standards
```{r echo=FALSE}
l2_auroc_sexps_plot_ts <- gkr %>% 
  ggplot(aes(x = median_spearman, y = auROC, color = method)) +
  geom_point() +
  xlab("Sample Similarity") +
  ylab("auROC") +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_auroc_sexps_plot_ts)
```

```{r echo=FALSE}
l2_auroc_sexps_cors_ts <- gkr %>% 
  group_by(method) %>% 
  summarise(correlation = cor(auROC, median_spearman, method = "pearson"))

datatable(l2_auroc_sexps_cors_ts, rownames = FALSE, filter="top", options = list(pageLength = 10, scrollX=T), 
          colnames = c("Method", "Pearson Correlation of auROC and Sample Similarity"))
```

## log<sub>2</sub>(precision/prior) at 20% recall {.tabset .tabset-fade .tabset-pills}

### Naive Standard
```{r echo=FALSE}
l2_prec_at_recall20_sexps_plot <- lrg_gnpr %>% 
  ggplot(aes(x = median_spearman, y = log2_precision_over_prior, color = method)) +
  geom_point() +
  xlab("Sample Similarity") +
  ylab("log2(precision/prior) at 20% recall") +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_prec_at_recall20_sexps_plot)
```

```{r echo=FALSE}
l2_prec_at_recall20_sexps_cors <- lrg_gnpr %>% 
  group_by(method) %>% 
  summarise(correlation = cor(log2_precision_over_prior, median_spearman, method = "pearson"))

datatable(l2_prec_at_recall20_sexps_cors, rownames = FALSE, filter="top", options = list(pageLength = 10, scrollX=T), 
          colnames = c("Method", "Pearson Correlation of log2(precision/prior) at 20% recall and Sample Similarity"))
```

### Tissue Specific Standards
```{r echo=FALSE}
l2_prec_at_recall20_sexps_plot_ts <- lrg_gkpr %>% 
  ggplot(aes(x = median_spearman, y = log2_precision_over_prior, color = method)) +
  geom_point() +
  xlab("Sample Similarity") +
  ylab("log2(precision/prior) at 20% recall") +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_prec_at_recall20_sexps_plot_ts)
```

```{r echo=FALSE}
l2_prec_at_recall20_sexps_cors_ts <- lrg_gkpr %>% 
  group_by(method) %>% 
  summarise(correlation = cor(log2_precision_over_prior, median_spearman, method = "pearson"))

datatable(l2_prec_at_recall20_sexps_cors_ts, rownames = FALSE, filter="top", options = list(pageLength = 10, scrollX=T), 
          colnames = c("Method", "Pearson Correlation of log2(precision/prior) at 20% recall and Sample Similarity"))
```

# Performance and Size Diversity {.tabset .tabset-fade .tabset-pills}
Size Diversity is calulated for a given experiment by taking the standard deviation of the sum of counts in each sample. 
## log<sub>2</sub>(auPRC/prior) {.tabset .tabset-fade .tabset-pills}

### Naive Standard
```{r echo=FALSE}
l2_auprc_prior_sizediv_plot <- gnr %>% 
  ggplot(aes(x = sqrt(counts_sample_sums_variance), y = log2_auprc_over_prior, color = method)) +
  geom_point() +
  xlab("Size Diversity") +
  ylab("log2(auPRC/prior)") +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_auprc_prior_sizediv_plot)
```

```{r echo=FALSE}
l2_auprc_prior_sizediv_cors <- gnr %>% 
  group_by(method) %>% 
  summarise(correlation = cor(log2_auprc_over_prior, sqrt(counts_sample_sums_variance), method = "pearson"))

datatable(l2_auprc_prior_sizediv_cors, rownames = FALSE, filter="top", options = list(pageLength = 10, scrollX=T), 
          colnames = c("Method", "Pearson Correlation of log2(auPRC/prior) and Size Diversity"))
```

### Tissue Specific Standards
```{r echo=FALSE}
l2_auprc_prior_sizediv_plot_ts <- gkr %>% 
  ggplot(aes(x = sqrt(counts_sample_sums_variance), y = log2_auprc_over_prior, color = method)) +
  geom_point() +
  xlab("Size Diversity") +
  ylab("log2(auPRC/prior)") +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_auprc_prior_sizediv_plot_ts)
```

```{r echo=FALSE}
l2_auprc_prior_sizediv_cors_ts <- gkr %>% 
  group_by(method) %>% 
  summarise(correlation = cor(log2_auprc_over_prior, sqrt(counts_sample_sums_variance), method = "pearson"))

datatable(l2_auprc_prior_sizediv_cors_ts, rownames = FALSE, filter="top", options = list(pageLength = 10, scrollX=T), 
          colnames = c("Method", "Pearson Correlation of log2(auPRC/prior) and Size Diversity"))
```

## auROC {.tabset .tabset-fade .tabset-pills}

### Naive Standard
```{r echo=FALSE}
l2_auroc_sizediv_plot <- gnr %>% 
  ggplot(aes(x = sqrt(counts_sample_sums_variance), y = auROC, color = method)) +
  geom_point() +
  xlab("Size Diversity") +
  ylab("auROC") +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_auroc_sizediv_plot)
```

```{r echo=FALSE}
l2_auroc_sizediv_cors <- gnr %>% 
  group_by(method) %>% 
  summarise(correlation = cor(auROC, sqrt(counts_sample_sums_variance), method = "pearson"))

datatable(l2_auroc_sizediv_cors, rownames = FALSE, filter="top", options = list(pageLength = 10, scrollX=T), 
          colnames = c("Method", "Pearson Correlation of auROC and Size Diversity"))
```

### Tissue Specific Standards
```{r echo=FALSE}
l2_auroc_sizediv_plot_ts <- gkr %>% 
  ggplot(aes(x = sqrt(counts_sample_sums_variance), y = auROC, color = method)) +
  geom_point() +
  xlab("Size Diversity") +
  ylab("auROC") +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_auroc_sizediv_plot_ts)
```

```{r echo=FALSE}
l2_auroc_sizediv_cors_ts <- gkr %>% 
  group_by(method) %>% 
  summarise(correlation = cor(auROC, sqrt(counts_sample_sums_variance), method = "pearson"))

datatable(l2_auroc_sizediv_cors_ts, rownames = FALSE, filter="top", options = list(pageLength = 10, scrollX=T), 
          colnames = c("Method", "Pearson Correlation of auROC and Size Diversity"))
```

## log<sub>2</sub>(precision/prior) at 20% recall {.tabset .tabset-fade .tabset-pills}

### Naive Standard
```{r echo=FALSE}
l2_prec_at_recall20_sizediv_plot <- lrg_gnpr %>% 
  ggplot(aes(x = sqrt(counts_sample_sums_variance), y = log2_precision_over_prior, color = method)) +
  geom_point() +
  xlab("Size Diversity") +
  ylab("log2(precision/prior) at 20% recall") +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_prec_at_recall20_sizediv_plot)
```

```{r echo=FALSE}
l2_prec_at_recall20_sizediv_cors <- lrg_gnpr %>% 
  group_by(method) %>% 
  summarise(correlation = cor(log2_precision_over_prior, sqrt(counts_sample_sums_variance), method = "pearson"))

datatable(l2_prec_at_recall20_sizediv_cors, rownames = FALSE, filter="top", options = list(pageLength = 10, scrollX=T), 
          colnames = c("Method", "Pearson Correlation of log2(precision/prior) at 20% recall and Size Diversity"))
```

### Tissue Specific Standards
```{r echo=FALSE}
l2_prec_at_recall20_sizediv_plot_ts <- lrg_gkpr %>% 
  ggplot(aes(x = sqrt(counts_sample_sums_variance), y = log2_precision_over_prior, color = method)) +
  geom_point() +
  xlab("Size Diversity") +
  ylab("log2(precision/prior) at 20% recall") +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_prec_at_recall20_sizediv_plot_ts)
```

```{r echo=FALSE}
l2_prec_at_recall20_sizediv_cors_ts <- lrg_gkpr %>% 
  group_by(method) %>% 
  summarise(correlation = cor(log2_precision_over_prior, sqrt(counts_sample_sums_variance), method = "pearson"))

datatable(l2_prec_at_recall20_sizediv_cors_ts, rownames = FALSE, filter="top", options = list(pageLength = 10, scrollX=T), 
          colnames = c("Method", "Pearson Correlation of log2(precision/prior) at 20% recall and Size Diversity"))
```

# Performance and Tissue {.tabset .tabset-fade .tabset-pills}
## log<sub>2</sub>(auPRC/prior) {.tabset .tabset-fade .tabset-pills}

### Naive Standard
```{r echo=FALSE}
l2_auprc_prior_tis_plot <- gnr %>% 
  ggplot(aes(x = tissue, y = log2_auprc_over_prior, color = method)) +
  geom_point() +
  xlab("Size Diversity") +
  ylab("log2(auPRC/prior)") +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_auprc_prior_tis_plot)
```
### Tissue Specific Standards
```{r echo=FALSE}
l2_auprc_prior_tis_plot_ts <- gkr %>% 
  ggplot(aes(x = tissue, y = log2_auprc_over_prior, color = method)) +
  geom_point() +
  xlab("Size Diversity") +
  ylab("log2(auPRC/prior)") +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_auprc_prior_tis_plot_ts)
```

## auROC {.tabset .tabset-fade .tabset-pills}

### Naive Standard
```{r echo=FALSE}
l2_auroc_tis_plot <- gnr %>% 
  ggplot(aes(x = tissue, y = auROC, color = method)) +
  geom_point() +
  xlab("Size Diversity") +
  ylab("auROC") +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_auroc_tis_plot)
```

### Tissue Specific Standards
```{r echo=FALSE}
l2_auroc_tis_plot_ts <- gkr %>% 
  ggplot(aes(x = tissue, y = auROC, color = method)) +
  geom_point() +
  xlab("Size Diversity") +
  ylab("auROC") +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_auroc_tis_plot_ts)
```

## log<sub>2</sub>(precision/prior) at 20% recall {.tabset .tabset-fade .tabset-pills}

### Naive Standard
```{r echo=FALSE}
l2_prec_at_recall20_tis_plot <- lrg_gnpr %>% 
  ggplot(aes(x = tissue, y = log2_precision_over_prior, color = method)) +
  geom_point() +
  xlab("Size Diversity") +
  ylab("log2(precision/prior) at 20% recall") +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_prec_at_recall20_tis_plot)
```

### Tissue Specific Standards
```{r echo=FALSE}
l2_prec_at_recall20_tis_plot_ts <- lrg_gkpr %>% 
  ggplot(aes(x = tissue, y = log2_precision_over_prior, color = method)) +
  geom_point() +
  xlab("Size Diversity") +
  ylab("log2(precision/prior) at 20% recall") +
  theme(panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_line(colour = "#999999", size = 0.1),
        panel.grid.minor = element_line(colour = "#999999", size = 0.1),
        text = element_text(size = 14))

ggplotly(l2_prec_at_recall20_tis_plot_ts)
```

